The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-24 paper/ms.tex
Two tables added: best fit parameters for Willott data (with/without dust attenuation)

Best fit parameters:

Cosmic Variance Dust Attenuation model:

$\log_{10}(L_0)$, mean value = 18.0668181805, 
cosmic std dev=0.0288558407431, 
mean sigma per box =0.115498563539

$\log_{10}(M_0)$, mean value = 11.1894829902, 
cosmic std dev=0.0718242117247, mean 
sigma per box =0.72909362196

$\beta$, mean value = 1.48014744519, 
cosmic std dev=0.175026973523, 
mean sigma per box =1.2988714515

$\gamma$, mean value = 0.402845130968, 
cosmic std dev=0.0575764062455, 
mean sigma per box =0.314709555486

\medskip

Cosmic Variance No-Dust Attenuation model:

$\log_{10}(L_0)$, mean value = 17.8076246968, 
cosmic std dev=0.0198125186745, 
mean sigma per box =0.150082796188

$\log_{10}(M_0)$, mean value = 11.119460579, 
smic std dev=0.0601358065131, 
mean sigma per box =0.642532804052

$\beta$, mean value = 1.43705896343, 
cosmic std dev=0.178253100134, 
mean sigma per box =1.37416358513

$\gamma$, mean value = 0.518242492031, 
cosmic std dev=0.0461244563387, 
mean sigma per box =0.245817572122

>>>>

\begin{table}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Parameter  & Mean value & Cosmic Variance & MCMC error\\\hline
$\log_{10}(L_0)$   & 18.067   & 0.029   & 0.116 \\
$\log_{10}(M_0)$  & 11.190   & 0.072   & 0.729 \\
$\beta$                  & 1.4801  & 0.175   & 1.299 \\
$\gamma$             & 0.40284 & 0.058  & 0.3147\\
\hline\hline
\end{tabular}
\caption{  Average Best fit parameters to the Willott data in the Dust Attenuation Model.} 
\label{table:Willott_best_fit_parameters}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Parameter  & Mean value & Cosmic Variance & MCMC error\\\hline
$\log_{10}(L_0)$   & 17.807   & 0.020   & 0.150 \\
$\log_{10}(M_0)$  & 11.119    & 0.060   & 0.642 \\
$\beta$                  &  1.437    & 0.178   & 1.374 \\
$\gamma$             &   0.518   & 0.046  & 0.246\\
\hline\hline
\end{tabular}
\caption{  Average Best fit parameters to the Willott data in the No-Dust Attenuation Model.} 
\label{table:Willott_best_fit_parameters_no_dust}
\end{center}
\end{table}
